
# Duplication duplication dupilcation...

Have you ever seen an R script that looks like this:

```{r}
data <- penguins

print(
  round(mean(subset(
    na.omit(data), species == "Adelie" & island == "Torgersen"
  )$bill_length_mm), 2)
)
print(
  round(mean(subset(
    na.omit(data), species == "Adelie" & island == "Biscoe"
  )$bill_length_mm), 2)
)
print(
  round(mean(subset(
    na.omit(data), species == "Adelie" & island == "Dream"
  )$bill_length_mm), 2)
)
```

The same thing is done 3 times: once for `Torgersen`, once for `Biscoe` and once for `Dream`.

This code is very hard to work with:

* __Hard to read__: that's a lot of code!
* __Hard to maintain__: if you want to change something, you will have to make the change 3 times.
* __Error prone__: one day, you will update all items and insert a bug in one. Or you will update an item and forget about the others.


It's time to **create a function**!

# What's a function
A function operates much like a factory.

Imagine it as a place where raw materials (**inputs**) are processed. Inside, various operations (**the function's code**) are performed, and voilà! Out comes a finished product (**the output**).

Everything starts with the _function name_. It includes a _verb_ since a function always _does_ something. Make the name self explanatory! For instance, `multiply_by_two` is much better than `function1`! We understand directly what it does.

Then comes the _assignment operator_ (<-) and the `function` keyword. The _arguments_ are provided here. You can have 0, 1 or several of them!

Last but not least comes the _body_ of the function where the work truly takes place. You can do whatever you want with your arguments, and end by returning your final result with `return()`.

# Example
The very first code chunk of this lesson computed the mean bill length for the 3 species of the dataset: `Torgersen`, `Biscoe` and `Dream`.

We can create a function called `calc_mean_bill` that expects 1 argument: the `island_name`. And then call the function 3 times, once for each island.

```{r}
calc_mean_bill <- function(island_name) {
  filtered_data <- subset(na.omit(data), species == "Adelie" & island == island_name)
  mean_bill_length <- mean(filtered_data$bill_length_mm)
  return(round(mean_bill_length, 2))
}

# Call the function for each island
calc_mean_bill("Torgersen")
calc_mean_bill("Biscoe")
calc_mean_bill("Dream")
```

# Learn by doing
As usual, there is no way you learn how functions work if you do not write them yourself.

Here is a list of exercises by growing order of complexity:
